---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1

column_numbers: 3
columnline_col: "#6F8196"
  

#ESSENTIALS
title: '**Kickstarter project**'
author:
  - name: '**Panema**'
    affil: 1
    main: true
  - name: Daniel Blanco
  - name: Georgia Barry
  - name: Benedicte Kjaerran
  
affiliation:
  - num: 1
    address: Bond University 
    author_textsize: 3em
primary_colour: "#6faef5"
secondary_colour: "white"
accent_colour: "#6F8196"
font_family: "Crimson Text"

main_findings:
  - "Kickstarter projects likeliness of success & what contributes to the success."

output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: 
    number_sections: false
bibliography: packages.bib
link-citations: true
---


```{r include=FALSE}
library(tidyr)
library(caret)
library(dplyr)
library(lubridate)
library(corrplot)
library("pROC")
library(modelr)
library("ggplot2")
library(RColorBrewer)
library(kableExtra)
library("arm")
library("car")
library("jtools")
library(pls)
library(glmnet)
library(MASS)
library("leaps")
library(caret)
library(kableExtra)
library("gmodels")
library("colorspace")

library(olsrr)
library(stats)
library(stats4)
library(statmod)

library(ggstance)
library(broom)
library("broom.mixed")

library("rmarkdown")
library("knitr")

```



```{r include=FALSE}
kickstarter <- readRDS("/Users/benedicte/Documents/Statistical regression/Group P/statistical-learning/final_clean_kickstarter.rds")

kickstarter$cat_child <- NULL
kickstarter$city <- NULL
kickstarter$blurb <- NULL
kickstarter$country_displayable_name <- NULL 
kickstarter$name <- NULL
kickstarter$deadline<-NULL 
kickstarter$launched_at<-NULL

cntnt_Europe = c("DK","AT", "BE", "CH","DE","ES", "FR", "GB","IE", "IT","LU", "NL","NO","SE")
cntnt_Asia = c("HK","JP","SG")
cntnt_NA = c("US","CA")
cntnt_SA = c("MX")
cntnt_Pacific = c("NZ","NZ")
#cntnt_NAmer =

eurpn <- kickstarter$country %in% cntnt_Europe
asian <- kickstarter$country %in% cntnt_Asia  
na <- kickstarter$country %in% cntnt_NA
sa <- kickstarter$country %in% cntnt_SA
pacific <- kickstarter$country %in% cntnt_Pacific

kickstarter$continent = "ph"
kickstarter$continent <- kickstarter$continent[eurpn] <- "Europe"
kickstarter$continent[asian] <- "Asia"
kickstarter$continent[na] <- "NorthAmerica"
kickstarter$continent[sa] <- "SouthAmerica"
kickstarter$continent[pacific] <- "Pacific"

kickstarter$continent <- as.factor(kickstarter$continent) 
kickstarter$backers_count_log <- log(kickstarter$backers_count+1)
kickstarter$backers_count <- NULL
kickstarter$country <- NULL

```

```{r warning=FALSE, include=FALSE}
confusionStats_df <- function(df,target){ # is as.character needed?
  cm <- confusionMatrix(table(Actual = df[[target]],Predicted = df$ClassPredict))
  return(data.frame(cbind(t(cm$overall),t(cm$byClass))))
}

predictLog <- function(df,log, thresh=0.5, t=T, f=F){
    
  p           <- predict(object = log, newdata = df,
                            type = "response",se.fit=T)
  df$fit      <- p$fit
  df$se.fit   <- p$se.fit
  df$logits   <- predict(object = log, newdata = df)
  df$ClassPredict <- ifelse(df$fit > thresh, t, f)
  return(df)
}
```

```{r warning=FALSE, include=FALSE}
IG_data <- kickstarter
IG_data$pledged <- NULL
IG_data$goal <- NULL
IG_data$pledged_log <-NULL
IG_data$id <- NULL
IG_data$target <- NULL
#IG_data$goal_ratio[IG_data$goal_ratio==0] <- min(IG_data$goal_ratio[IG_data$goal_ratio>0]) *0.9
IG_data$goal_ratio <- IG_data$goal_ratio +1
min(IG_data$goal_ratio)
```

```{r warning=FALSE, include=FALSE}
IG <-glm(goal_ratio ~ + cat_parent+ month+ number_of_days +
     backers_count_log + continent +(staff_pick) * (goal_log),family=inverse.gaussian(link=log), data=IG_data)
```



```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction of kickstarter 

Kickstarter is an online crowdfunding platform that provides an ‘all-or-nothing’ approach to project funding. A sample of five years of Kickstarter data, from April 2020 to April 2015, was obtained to make inferences for Kickstarter campaigns.The aim of our research was to provide models that predict the success of a project launched on Kickstarter, predict what factors are likely to increase percentage of a campaigns pledged amount over its goal, and how can the probability of success, or goal ratio, for a given Kickstarter campaign be assessed.

```{r echo=FALSE, fig.align=, fig.height=6, fig.width=12}
status.freq1 <- kickstarter %>%
  group_by(target) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

status.freq1$target <- factor(status.freq1$target, levels = status.freq1$target)
ggplot(status.freq1, aes(target, count, fill = count)) +
  geom_bar(stat = "identity") +
  ggtitle("Projects by Outcome") +
  xlab("Project Outcome") +
  ylab("Frequency") +
  geom_text(aes(label = count), vjust = -0.5) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(size = 11, angle = 90),
    legend.position = "null"
  ) +
  scale_fill_gradient(low = "lightskyblue", high = "royalblue4")
```

```{r echo=FALSE, warning=FALSE}
# Success vs. Fail by Country
ggplot(kickstarter) +
  aes(x = continent, fill = target) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "continent", y = "Proportion", 
       title = "Success vs. Failed Kickstarter Campaigns by continent", 
       subtitle = "as proportion", fill = "Outcome:") +
  coord_flip() +
  theme_minimal()
```
 

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

This report aims to analyse data sourced from Kickstarter and provide models that answer the following questions: 

1. What factors are likely to increase percentage of a campaigns pledged amount over its goal (goal_ratio)?

2. What factors influence the success or failure of a project launched on Kickstarter?

3. How can the probability of success, or goal ratio, for a given Kickstarter campaign be assessed?

# Methods
GLM Inverse Gaussian & Binomial were used to create the models. 
The data was preprocced before by removing and changing some of the variables. 

```{r eval=FALSE, warning=FALSE, include=FALSE}
ggplot(kickstarter, aes(x = kickstarter$goal_ratio, y = staff_pick)) + geom_area(alpha = 0.6) + scale_fill_brewer(palette = "Harmonic")


```

The most significant factor for increasing the likelihood of success is backers_count_log.
```{r echo=FALSE, warning=FALSE}
ggplot(kickstarter, aes(x = kickstarter$backers_count_log, fill = target)) + geom_density(alpha = 0.6) + scale_fill_discrete_qualitative(palette = "Harmonic")
```

# Results of the Gaussian Model 

The residual plot 

```{r, residual IG, fig.cap='Residual plot of IG model', out.width="80%"}
plot(IG$linear.predictors,residuals(IG,type="deviance"),pch=16, col = "royalblue4")
```


Confidence intervalls with 95% confidence for the Gaussian Model  

```{r confidence interval, echo=FALSE, fig.cap='confidence intervalls', fig.height=6, warning=FALSE, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))

coef(IG)[2] + 1.96*c(-1,1)*summary(IG)$coef[2,2]

plot_summs(IG, scale = TRUE, plot.distributions = TRUE, inner_ci_level = .95)+ add_y_gridlines(T)

```



## Binominal model results 

```{r warning=FALSE, include=FALSE}
bi_data <- kickstarter
bi_data$pledged <- NULL
bi_data$goal <- NULL
bi_data$pledged_log <-NULL
bi_data$id <- NULL
bi_data$goal_ratio <- NULL

binominal_baseline <- glm(target ~., data = bi_data, family = binomial)
binominal_baseline <-step(binominal_baseline,trace=FALSE)
```

```{r Binominal, echo=FALSE, out.width = "8cm", out.height= "5cm", warning=FALSE}
#,booktabs = TRUE
results <- predictLog(bi_data, binominal_baseline, t="successful", f="failed")

results$ClassPredict <- as.factor(results$ClassPredict)

confusionStats_df(results,"target")[c("Accuracy","Sensitivity","Specificity","Precision")]

knitr::kable(confusionStats_df(results,"target")[c("Accuracy","Sensitivity","Specificity","Precision")]* 100, digits = 2, format = "html", caption = "Model performance in percentage") %>%
  kable_styling(font_size = 14, full_width = T)%>%
  kable_styling(bootstrap_options = c("striped", "scale_down", "hover"))%>%
  kable_styling(fixed_thead=list(enabled = T, background = "lightskyblue"))

```

Since the Binominal model was built using Step AIC, and interactions did not improve the residual plot, we expected it to be less bias. The results show that this Binominal model is less bias with 58% of the predictions being “successful” and the actual data having 56.67% “successful” campaigns.
```{r residual binominal, echo=FALSE, warning=FALSE, out.width="80%"}
arm:::binnedplot(results$fit, as.numeric(results$target) - as.numeric(results$ClassPredict), col.pts = "royalblue4", col.int = "lightskyblue")
```


```{r ROC , echo=FALSE,fig.height=6, warning=FALSE, out.width="80%"}
plot.roc(results$target,results$fit, col = "royalblue4",
         main = "Binominal baseline model", print.auc = TRUE)
```

The confidence intervalls with 95% confidence for the binominal model 
```{r confidence binominal, echo=FALSE, warning=FALSE}
coef(binominal_baseline)[2] + 1.96*c(-1,1)*summary(binominal_baseline)$coef[2,2]

plot_summs(binominal_baseline, scale = TRUE, plot.distributions = TRUE, inner_ci_level = .95)
```



# Conclusion 

The goal_ratio predictions are much more conservative than the probability predictions, meaning goal_ratio will likely be understated.

Probability predictions from the binomial model were directionally correct 94.49% of the times. Area Under Curve (AUC) represents a models aggregate ability to discriminate between the two categories. The binomial models AUC of 0.987 confirms it is more than suitable for predicting “Successful” or “failure” of Kickstarter campaigns. Looking at the residual plot for the binomial model, campaigns near the 50% region should not be trusted due to increased variance. Further investigations found that probability predictions near the 50% mark are rare (5% of predictions) , so this should not be an issue fore most using the model.

Anyone starting a Kickstarter campaign should benefit from the conservative goal_ratio predictions with the probability predictions. Additionally, an understanding of the coefficients that increase the goal_ratio and probability of success improve planning for campaigns. The appendix of this report provides useful visualizations of the data that complement the findings of this report and provide more useful context for anyone considering a Kickstarter campaign. The visual aids convey understanding to the distributions of the data that may effect the models conclusions in regard to a campaigns. Additionally, a nice visualization of the models coefficient values, along with 95% confidence intervals, is provided. The coefficient values visual helps conceptualize what features have a more adverse or positive effect with less difficulty than looking at the raw numbers. Simply put, the larger coefficient values have a positive impact, and negative values have an adverse impact on probabilities or goal_ratio.


# References
Kickstarter. (2020, July 20). Kickstarter Stats. Retrieved from Kickstarter: https://www.kickstarter.com/help/stats 

Web Robots. (2020, July). Kickstarter Datasets. Retrieved from Web Robots: https://webrobots.io/kickstarter-datasets/ 